Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-20 Draft.Rmd
Update Draft.Rmd

## Wrangling
```{r Predictors}
# Split origin dataset into 80/20
dat_split <- initial_split(origin, prop =.8)
dat_split

@@

```{r Random Forests}
# Create Random Forest Model
model4 <- rand_forest(mtry = 5) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")

# Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)

>>>>

## Wrangling
```{r Predictors}
set.seed(123)
# Split origin dataset into 80/20
dat_split <- initial_split(origin, prop =.8)
dat_split

@@

# Create Random Forest Model
set.seed(123)
# Create Random Forest Model
# Use grid of tuning parameters
model4 <- rand_forest(mtry = tune("mtry"),
                     min_n = tune("min_n")) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")
# Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)

# Fit the model on the full training dataset using the `fit()` function
res4 <- fit(wf4, data = train_scaled)
# Check performance on the complete training data
res4 %>% 
    extract_fit_engine() %>% 
    summary()
# Check performance using cross-validation
folds4 <- vfold_cv(train, v = 10)
folds4
# Determine performance of model by resampling
res4 <- fit_resamples(wf4, folds4) # ERROR Assigned data `orig_rows` must be compatible with existing data.
res4 %>% 
    collect_metrics()

## Try a grid of tuning parameters
model <- rand_forest(mtry = tune("mtry"),
                     min_n = tune("min_n")) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")

wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model)

## Fit model over grid of tuning parameters
res <- tune_grid(wf4, resamples = folds4, grid = 20)

res %>% 
    collect_metrics()
